Trends of SDR in Thessaloniki

### 2023-11-02 MDPI_submition.Rmd
Commit 2023-11-02 14:14

---
title: Full title of the paper (Capitalized)
author:
  - name:  Athanasios Natsis
    affil: 1,* # \ddagger
    orcid: 0000-0002-5199-4119
  - name: Alkiviadis Bais
    affil: 2, #\dagger, # \ddagger
affiliation:
  - num: 1
    address: |
      Aristotle University of Thessaloniki - 
      Laboratory of Atmospheric Physics,
      Campus Box 149, 54124 Thessaloniki, Greece
    email: natsisphysicist@gmail.com
  - num: 2
    address: |
      Your department
      Street, City, Country
#     email: abais@auth.gr
# author citation list in chicago format
authorcitation: |
  Natsis, A.; Bais, A.
# firstnote to eighthnote
# firstnote: |
#   Current address: Updated affiliation
# secondnote: |
#   These authors contributed equally to this work.
correspondence: |
  natsisphysicist@gmail.com;
#   Tel.: +XX-000-00-0000.
# document options
journal: applsci
type:    article
status:  submit
# front matter
simplesummary: |
  A Simple summary goes here.
abstract: |
  The shortwave downward solar irradiance (SDR) is an important factor that drives climate processes, production and can affect all living organisms.
  While monitoring the long term variability, there are observations of upward and downward SDR trends on different locations around the world for different time periods.
  Periods of positive tredns are refered as brightening periods and with negative tredns as dimming periods.
  We studied 29 years of CM-21 data from Thessaloniki, Greece, under three sky conditions (clear sky, cloudy sky and all sky conditions), applying a cloud sky identification algorithm.
  We found a positive trend for all-sky and clear-sky conditions, and also, investigated the consistency of those trends, the effect of the solar zenith angle, and the variation of the trends for the seasons of the year.
  We indentified that there are some anomalies in the long term SDR trends, for all sky conditions.
# back matter
keywords: |
  GHI; SDR; Solar Brigthening/Dimming (list three to ten pertinent keywords specific 
  to the article, yet reasonably common within the subject discipline.).
acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly 
  indicate grants that you have received in support of your research work. 
  Clearly state if you received funds for covering the costs to publish in open 
  access.
authorcontributions: |
  For research articles with several authors, a short paragraph specifying their 
  individual contributions must be provided. The following statements should be 
  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
  limited to those who have contributed substantially to the work reported.
funding: |
  Please add: ``This research received no external funding'' or ``This research 
  was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded 
  by XXX''. Check carefully that the details given are accurate and use the 
  standard spelling of funding agency names at 
  \url{https://search.crossref.org/funding}, any errors may affect your future 
  funding.
institutionalreview: |
  In this section, you should add the Institutional Review Board Statement and 
  approval number, if relevant to your study. You might choose to exclude 
  this statement if the study did not require ethical approval. Please note 
  that the Editorial Office might ask you for further information. Please add 
  “The study was conducted in accordance with the Declaration of Helsinki, 
  and approved by the Institutional Review Board (or Ethics Committee) of 
  NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies 
  involving humans. OR “The animal study protocol was approved by the 
  Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE 
  (protocol code XXX and date of approval).” for studies involving animals. 
  OR “Ethical review and approval were waived for this study due to REASON 
  (please provide a detailed justification).” OR “Not applicable” for
   studies not involving humans or animals.
# informedconsent: |
#   Any research article describing a study involving humans should contain this 
#   statement. Please add ``Informed consent was obtained from all subjects 
#   involved in the study.'' OR ``Patient consent was waived due to REASON 
#   (please provide a detailed justification).'' OR ``Not applicable'' for 
#   studies not involving humans. You might also choose to exclude this statement 
#   if the study did not involve humans.
#   
#   Written informed consent for publication must be obtained from participating 
#   patients who can be identified (including by the patients themselves). Please 
#   state ``Written informed consent has been obtained from the patient(s) to 
#   publish this paper'' if applicable.
dataavailability: |
  We encourage all authors of articles published in MDPI journals to share 
  their research data. In this section, please provide details regarding where 
  data supporting reported results can be found, including links to publicly 
  archived datasets analyzed or generated during the study. Where no new data 
  were created, or where data is unavailable due to privacy or ethical 
  re-strictions, a statement is still required. Suggested Data Availability 
  Statements are available in section “MDPI Research Data Policies” at 
  \url{https://www.mdpi.com/ethics}.
conflictsofinterest: |
  Declare conflicts of interest or state 'The authors declare no conflict of 
  interest.' Authors must identify and declare any personal circumstances or
  interest that may be perceived as inappropriately influencing the
  representation or interpretation of reported research results. Any role of the
  funding sponsors in the design of the study; in the collection, analyses or 
  interpretation of data in the writing of the manuscript, or in the decision to 
  publish the results must be declared in this section. If there is no role, 
  please state 'The founding sponsors had no role in the design of the study; 
  in the collection, analyses, or interpretation of data; in the writing of the 
  manuscript, an in the decision to publish the results'.
# sampleavailability: |
#   Samples of the compounds ...... are available from the authors.
supplementary: |
 The following supporting information can be downloaded at:  
 \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.
abbreviations:
  - short: DNI
    long: Direct beam/normal irradiance
  - short: CSid
    long: Clear sky identification algorithm
  - short: CUSUM
    long: Cumulative sum
  - short: SDR 
    long: Solar downward radiation
  - short: SZA
    long: Solar zenith angle

header-includes:
   # - \usepackage{subfig}
   - \usepackage{subcaption}
   - \captionsetup[sub]{position=bottom, labelfont={bf, small, stretch=1.17}, labelsep=space, textfont={small, stretch=1.5}, aboveskip=6pt,  belowskip=6pt, singlelinecheck=off, justification=justified} 
bibliography: manualreferences.bib
appendix:     appendix.tex
endnotes:     false
output: 
  rticles::mdpi_article:
    extra_dependencies:  longtable 
    keep_tex:            yes

---

@@

x_latex %>%
    collapse_rows(columns = 1, valign = "middle", latex_hline = "custom") %>%
    kable_styling(latex_options = c('striped', 'hold_position'), full_width = TRUE) %>%
    # kable_styling(full_width = T) %>%
    # kable_styling("striped")      %>%
    column_spec(1, width = "8em")

>>>>

---
title:     "Trends of SDR in Thessaloniki"
author:
  - name:  Athanasios Natsis
    affil: 1,* # \ddagger
    orcid: 0000-0002-5199-4119
  - name: Alkiviadis Bais
    affil: 2, #\dagger, # \ddagger
affiliation:
  - num: 1
    address: |
      Aristotle University of Thessaloniki - 
      Laboratory of Atmospheric Physics,
      Campus Box 149, 54124 Thessaloniki, Greece
    email: natsisphysicist@gmail.com
  - num: 2
    address: |
      Your department
      Street, City, Country
#     email: abais@auth.gr
# author citation list in chicago format
authorcitation: |
  Natsis, A.; Bais, A.
# firstnote to eighthnote
# firstnote: |
#   Current address: Updated affiliation
# secondnote: |
#   These authors contributed equally to this work.
correspondence: |
  natsisphysicist@gmail.com;
#   Tel.: +XX-000-00-0000.

# document options
journal: applsci
type:    article
status:  submit

# front matter
simplesummary: |
  A Simple summary goes here.

abstract: |
  The shortwave downward solar irradiance (SDR) is an important factor that drives climate processes, production and can affect all living organisms.
  While monitoring the long term variability, there are observations of upward and downward SDR trends on different locations around the world for different time periods.
  Periods of positive tredns are refered as brightening periods and with negative tredns as dimming periods.
  We studied 29 years of CM-21 data from Thessaloniki, Greece, under three sky conditions (clear sky, cloudy sky and all sky conditions), applying a cloud sky identification algorithm.
  We found a positive trend for all-sky and clear-sky conditions, and also, investigated the consistency of those trends, the effect of the solar zenith angle, and the variation of the trends for the seasons of the year.
  We indentified that there are some anomalies in the long term SDR trends, for all sky conditions.

# back matter
keywords: |
  GHI; SDR; Solar Brigthening/Dimming.
## list three to ten pertinent keywords specific to the article, yet reasonably common within the subject discipline

acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly 
  indicate grants that you have received in support of your research work. 
  Clearly state if you received funds for covering the costs to publish in open 
  access.

authorcontributions: |
  For research articles with several authors, a short paragraph specifying their 
  individual contributions must be provided. The following statements should be 
  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
  limited to those who have contributed substantially to the work reported.

funding: |
  Please add: ``This research received no external funding'' or ``This research 
  was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded 
  by XXX''. Check carefully that the details given are accurate and use the 
  standard spelling of funding agency names at 
  \url{https://search.crossref.org/funding}, any errors may affect your future 
  funding.

# institutionalreview: |
#   In this section, you should add the Institutional Review Board Statement and 
#   approval number, if relevant to your study. You might choose to exclude 
#   this statement if the study did not require ethical approval. Please note 
#   that the Editorial Office might ask you for further information. Please add 
#   “The study was conducted in accordance with the Declaration of Helsinki, 
#   and approved by the Institutional Review Board (or Ethics Committee) of 
#   NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies 
#   involving humans. OR “The animal study protocol was approved by the 
#   Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE 
#   (protocol code XXX and date of approval).” for studies involving animals. 
#   OR “Ethical review and approval were waived for this study due to REASON 
#   (please provide a detailed justification).” OR “Not applicable” for
#    studies not involving humans or animals.

# informedconsent: |
#   Any research article describing a study involving humans should contain this 
#   statement. Please add ``Informed consent was obtained from all subjects 
#   involved in the study.'' OR ``Patient consent was waived due to REASON 
#   (please provide a detailed justification).'' OR ``Not applicable'' for 
#   studies not involving humans. You might also choose to exclude this statement 
#   if the study did not involve humans.
#   
#   Written informed consent for publication must be obtained from participating 
#   patients who can be identified (including by the patients themselves). Please 
#   state ``Written informed consent has been obtained from the patient(s) to 
#   publish this paper'' if applicable.

dataavailability: |
  We encourage all authors of articles published in MDPI journals to share 
  their research data. In this section, please provide details regarding where 
  data supporting reported results can be found, including links to publicly 
  archived datasets analyzed or generated during the study. Where no new data 
  were created, or where data is unavailable due to privacy or ethical 
  re-strictions, a statement is still required. Suggested Data Availability 
  Statements are available in section “MDPI Research Data Policies” at 
  \url{https://www.mdpi.com/ethics}.

# conflictsofinterest: |
#   Declare conflicts of interest or state 'The authors declare no conflict of 
#   interest.' Authors must identify and declare any personal circumstances or
#   interest that may be perceived as inappropriately influencing the
#   representation or interpretation of reported research results. Any role of the
#   funding sponsors in the design of the study; in the collection, analyses or 
#   interpretation of data in the writing of the manuscript, or in the decision to 
#   publish the results must be declared in this section. If there is no role, 
#   please state 'The founding sponsors had no role in the design of the study; 
#   in the collection, analyses, or interpretation of data; in the writing of the 
#   manuscript, an in the decision to publish the results'.

# sampleavailability: |
#   Samples of the compounds ...... are available from the authors.

supplementary: |
 The following supporting information can be downloaded at:  
 \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.

abbreviations:
  - short: DNI
    long: Direct beam/normal irradiance
  - short: CSid
    long: Clear sky identification algorithm
  - short: CUSUM
    long: Cumulative sum
  - short: SDR 
    long: Solar downward radiation
  - short: SZA
    long: Solar zenith angle

header-includes:
   # - \usepackage{subfig}
   - \usepackage{subcaption}
   - \captionsetup[sub]{position=bottom, labelfont={bf, small, stretch=1.17}, labelsep=space, textfont={small, stretch=1.5}, aboveskip=6pt,  belowskip=6pt, singlelinecheck=off, justification=justified}

bibliography: manualreferences.bib

appendix:     appendix.tex

endnotes:     false

output: 
  rticles::mdpi_article:
    extra_dependencies:  longtable 
    keep_tex:            yes
  bookdown::word_document2: default
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      yes
    keep_tex:         no
    latex_engine:     xelatex
    toc:              no
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
    documentclass:    article
    classoption:      a4paper,oneside
    fontsize:         12pt
    geometry:         "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
    link-citations:   yes
    colorlinks:       yes
    urlcolor:         blue
    biblio-style:     apalike
---

@@

x_latex %>%
    collapse_rows(columns = 1, valign = "middle", latex_hline = "custom")           %>%
    kable_styling(latex_options = c('striped', 'hold_position'), full_width = TRUE) %>%
    column_spec(1, width = "8em")

### 2023-11-02 MDPI_submition.tex
Commit 2023-11-02 14:14

%=================================================================
% Full title of the paper (Capitalized)
\Title{Full title of the paper (Capitalized)}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Full title of the paper (Capitalized)}

@@

% Keywords
\keyword{GHI; SDR; Solar Brigthening/Dimming (list three to ten
pertinent keywords specific to the article, yet reasonably common within
the subject discipline.).}

@@

\institutionalreview{In this section, you should add the Institutional
Review Board Statement and approval number, if relevant to your study.
You might choose to exclude this statement if the study did not require
ethical approval. Please note that the Editorial Office might ask you
for further information. Please add ``The study was conducted in
accordance with the Declaration of Helsinki, and approved by the
Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE
(protocol code XXX and date of approval).'' for studies involving
humans. OR ``The animal study protocol was approved by the Institutional
Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code
XXX and date of approval).'' for studies involving animals. OR ``Ethical
review and approval were waived for this study due to REASON (please
provide a detailed justification).'' OR ``Not applicable'' for studies
not involving humans or animals.}

@@

\conflictsofinterest{Declare conflicts of interest or state `The authors
declare no conflict of interest.' Authors must identify and declare any
personal circumstances or interest that may be perceived as
inappropriately influencing the representation or interpretation of
reported research results. Any role of the funding sponsors in the
design of the study; in the collection, analyses or interpretation of
data in the writing of the manuscript, or in the decision to publish the
results must be declared in this section. If there is no role, please
state `The founding sponsors had no role in the design of the study; in
the collection, analyses, or interpretation of data; in the writing of
the manuscript, an in the decision to publish the results'.}

@@

\noindent
\begin{tabular}{@{}ll}
DNI & Direct beam/normal irradiance \\
CSid & Clear sky identification algorithm \\
CUSUM & Cumulative sum \\
SDR & Solar downward radiation \\
\end{tabular}}

>>>>

%=================================================================
% Full title of the paper (Capitalized)
\Title{Trends of SDR in Thessaloniki}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Trends of SDR in Thessaloniki}

@@

% Keywords
\keyword{GHI; SDR; Solar Brigthening/Dimming.}

@@

@@

@@

\noindent
\begin{tabular}{@{}ll}
DNI & Direct beam/normal irradiance \\
CSid & Clear sky identification algorithm \\
CUSUM & Cumulative sum \\
SDR & Solar downward radiation \\
SZA & Solar zenith angle \\
\end{tabular}}
